Aligning marine species range data to better serve science and conservation

### 2016-06-15 manuscript-main-j_app_ecol.Rmd
tweakin a few things to clean up

---
title: "Aligning marine species range data to better serve science and conservation"
author: Casey O'Hara^1^, Jamie C. Afflerbach^1^, Courtney Scarborough^1^, Benjamin
  S. Halpern^1,2,3^
csl: refs/ecology-letters.csl
output:
  word_document: default
  pdf_document:
    number_sections: no
    toc: no
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
bibliography: refs/zotero_lib.bib
---

@@

``` {r abstract, child = 'ms_1_abst_150wd.Rmd'}
```

>>>>

---
title: "Aligning marine species range data to better serve science and conservation"
author: Casey O'Hara^1^, Jamie C. Afflerbach^1^, Courtney Scarborough^1^, Benjamin
  S. Halpern^1,2,3^
csl: refs/journal-of-applied-ecology.csl
output:
  word_document: default
  pdf_document:
    number_sections: no
    toc: no
  html_document:
    highlight: haddock
    number_sections: no
    theme: spacelab
    toc: no
bibliography: refs/zotero_lib.bib
---

@@

``` {r abstract, child = 'ms_1_abst_j_appl_ecol.Rmd'}
```
